### 2015-04-13 related.tex
"tech report" --> "technical report"

Our contract language and system model is inspired by the axiomatic
description of RDT semantics proposed in~\cite{Burckhardt2014}. While
~\cite{Burckhardt2014} uses axioms for formal verification of
an RDT implementation, we utilize them as a means for the user to express
desired consistency guarantees in the application. The operational semantics
of \name (described in the accompanying tech report~\cite{techrep}) describes
an operational manifestation of our system model. \cite{Burckhardt2015} also
presents an operational model of a replicated data store that is based on
the abstract system model presented in ~\cite{Burckhardt2014}. Their claims
about the expressivity and practicality of the system model vindicate
ours. However, both approaches differ in the way they aim to empower the application
programmer. \cite{Burckhardt2015} exposes the operational model to the
programmer, along with primitives, such as \cf{push}, \cf{pull}
and \cf{fetch}, that make it easy to \emph{implement} required
consistency and isolation guarantees. In contrast, \name completely
abstracts its operational model, and instead relies on contract
classification to automatically \emph{choose} appropriate consistency and isolation
levels. Similar to~\cite{Burckhardt2014} and~\cite{Burckhardt2015}, our
system model does not incorporate real (i.e., wall-clock) time. Hence, our
contract language cannot describe store semantics such as recency or
bounded-staleness guarantees offered by certain stores~\cite{Pileus}.

>>>>

Our contract language and system model is inspired by the axiomatic description
of RDT semantics proposed in~\cite{Burckhardt2014}. While ~\cite{Burckhardt2014}
uses axioms for formal verification of an RDT implementation, we utilize them as
a means for the user to express desired consistency guarantees in the
application. The operational semantics of \name (described in the accompanying
technical report~\cite{techrep}) describes an operational manifestation of our
system model. \cite{Burckhardt2015} also presents an operational model of a
replicated data store that is based on the abstract system model presented in
~\cite{Burckhardt2014}. Their claims about the expressivity and practicality of
the system model vindicate ours. However, both approaches differ in the way they
aim to empower the application programmer. \cite{Burckhardt2015} exposes the
operational model to the programmer, along with primitives, such as \cf{push},
\cf{pull} and \cf{fetch}, that make it easy to \emph{implement} required
consistency and isolation guarantees. In contrast, \name completely abstracts
its operational model, and instead relies on contract classification to
automatically \emph{choose} appropriate consistency and isolation levels.
Similar to~\cite{Burckhardt2014} and~\cite{Burckhardt2015}, our system model
does not incorporate real (i.e., wall-clock) time. Hence, our contract language
cannot describe store semantics such as recency or bounded-staleness guarantees
offered by certain stores~\cite{Pileus}.
